Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-10 paper/tex/introduction.tex
macros

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability $p(z)$ as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative $\chi^{2}$ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

>>>>

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability $p(z)$ as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.
